### 2024-01-14 tesis_Ashish/Acknowledgement/acknowledgement.tex
Updated thesis 14 Jan 2024

I would like to express my sincere gratitude to all those who have supported and guided me throughout my journey in completing my PhD thesis in particle physics, specifically focusing on the CMS experiment at CERN. Their unwavering support, encouragement, and expertise have been invaluable to my success.

First and foremost, I would like to extend my deepest appreciation to my esteemed thesis supervisor, Dr. Jose Feliciano Benitez. His exceptional guidance, profound knowledge, and unwavering commitment to scientific exploration have shaped my research endeavors and allowed me to delve into the fascinating world of particle physics. His mentorship and continuous support have been instrumental in every step of my thesis, from conceptualization to the final stages of completion. I am truly grateful for the opportunity to work under his supervision, and I have grown immensely both as a researcher and as an individual thanks to his invaluable guidance.

I would also like to express my heartfelt gratitude to my loving parents, whose unconditional love, encouragement, and sacrifices have been the cornerstone of my academic journey. Their unwavering belief in my abilities and their constant support have given me the strength and motivation to overcome challenges and pursue my passion for scientific exploration. I am eternally grateful for their constant presence in my life and their unwavering support throughout this demanding academic endeavor.

Furthermore, I would like to extend my appreciation to my sisters for their unwavering encouragement, understanding, and motivation during the course of my PhD. Their belief in my abilities and their continuous support have been an immense source of inspiration and strength, reminding me to remain focused and determined even during the most challenging times.

I would also like to acknowledge the collective efforts of the scientific community at CERN and all those who have contributed to the CMS experiment. Their collaboration, expertise, and dedication have created an enriching environment for research and have allowed me to be a part of groundbreaking discoveries in the field of particle physics.

Lastly, I am deeply grateful to all my friends and colleagues who have provided valuable insights, stimulating discussions, and endless support throughout this journey. Their encouragement, camaraderie, and intellectual exchanges have played a significant role in shaping my research and personal growth.

To each and every person mentioned above, as well as those who may not be named individually, I offer my sincerest thanks. Your contributions have been invaluable, and I am humbled by the generosity and unwavering support I have received. This thesis would not have been possible without your guidance, encouragement, and belief in me.

Thank you from the bottom of my heart.

>>>>

I wish to express my profound gratitude to all those who have supported and guided me throughout my journey towards completing my PhD thesis in particle physics, with a focus on the CMS experiment at CERN. Their unwavering support, encouragement, and expertise have been indispensable to my success.

Foremost, I extend my deepest appreciation to my esteemed thesis supervisor, Dr. Jose Feliciano Benitez. His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors. Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuous support has been pivotal at every stage of my thesis. I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I have experienced through his invaluable guidance.

My heartfelt gratitude goes to my parents, Omkar Jagtaran Singh and Anita. Their unconditional love, encouragement, and sacrifices have been the bedrock of my academic journey. Their unwavering belief in my abilities and constant support have been my source of strength and motivation, enabling me to overcome challenges and pursue my passion for scientific exploration. Their constant presence and support throughout this demanding academic endeavor are cherished and deeply appreciated.

I also extend my appreciation to my sisters Priya, Monu, Sonu, Reena, and Seema. Their unwavering encouragement, understanding, and motivation have been an immense source of inspiration. Their belief in my abilities and continuous support have been a pillar of strength, urging me to remain focused and resilient even during challenging times.

I am thankful for the collective efforts of the scientific community at CERN and all contributors to the CMS experiment. Their collaboration, expertise, and dedication have fostered an enriching research environment, allowing me to partake in groundbreaking discoveries in particle physics.

I am indebted to my friends and colleagues, especially Rohit Gupta, for their valuable insights, stimulating discussions, and enduring support. Their encouragement, camaraderie, and intellectual exchanges have been instrumental in shaping both my research and personal growth.

To everyone mentioned, and those unnamed but equally appreciated, I extend my sincerest thanks. Your contributions, large and small, have been invaluable, and I am humbled by the generosity and support I have received. This thesis stands as a testament to your guidance, encouragement, and belief in my potential.

From the bottom of my heart, thank you.

### 2024-01-14 tesis_Ashish/Dedication/dedication.tex
Updated thesis 14 Jan 2024

I wish to express my profound gratitude to all those who have supported and guided me throughout my journey towards completing my PhD thesis in particle physics, with a focus on the CMS experiment at CERN. Their unwavering support, encouragement, and expertise have been indispensable to my success.

Foremost, I extend my deepest appreciation to my esteemed thesis supervisor, Dr. Jose Feliciano Benitez. His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors. Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuous support has been pivotal at every stage of my thesis. I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I have experienced through his invaluable guidance.

@@

I am thankful for the collective efforts of the scientific community at CERN and all contributors to the CMS experiment. Their collaboration, expertise, and dedication have fostered an enriching research environment, allowing me to partake in groundbreaking discoveries in particle physics.

I am indebted to my friends and colleagues, especially Rohit Gupta, for their valuable insights, stimulating discussions, and enduring support. Their encouragement, camaraderie, and intellectual exchanges have been instrumental in shaping both my research and personal growth.

To everyone mentioned, and those unnamed but equally appreciated, I extend my sincerest thanks. Your contributions, large and small, have been invaluable, and I am humbled by the generosity and support I have received. This thesis stands as a testament to your guidance, encouragement, and belief in my potential.

From the bottom of my heart, thank you.

>>>>

\begin{dedication}
\begin{center}
    \section*{Acknowledgements}
\end{center}
\justify{

I wish to express my profound gratitude to all those who have supported and guided me throughout my journey towards completing my PhD thesis in high energy particle physics, with a focus on the CMS experiment at CERN. Their unwavering support, encouragement, and expertise have been indispensable to my success.

Foremost, I extend my deepest appreciation to my esteemed thesis supervisor, Dr. Jose Feliciano Benitez. His exceptional guidance, profound knowledge, and commitment to scientific exploration have profoundly shaped my research endeavors. Delving into the fascinating world of particle physics under his mentorship has been a privilege, and his continuoussupport has been pivotal at every stage of my thesis. I am immensely grateful for the opportunity to work under his supervision and for the personal and professional growth I h\
ave experienced through his invaluable guidance.

@@

I am indebted to my friends and colleagues, especially Rohit Gupta and Mohammad Balal, for their valuable insights, stimulating discussions, and enduring support. Their encouragement, camaraderie,and intellectual exchanges have been instrumental in shaping both my research and personal growth.

Finally, I would like to thank  University of Sonora and CONACYT for providing finnacial support to my research.

%I would like to thank my wife El\'izabeth for her unconditional support in the challenges I set for myself, without her this would not be possible. To my advisor, Dr. Jos\'e Ben\'itez, for giving me guidance, patience and, above all, the opportunity to work in such a professional team and join the CMS experiment, that was a dream for me. To the University of Sonora and CONACYT for supporting me in completing this important challenge in my professional career.

\end{dedication}
